Status and Best Practices for Reproducible Research In Plant Pathology

### 2018-01-10 inst/paper/Sparks_et_al-main_text.Rmd
Verbage around point for writing

### Repository
- Using GitHub for code (and small data?)
- Using Figshare or Zenodo vs a lab website (DOIs, other reasons)
- Most ideal a library or other proper long-term data archival service

>>>>

### Repository
- Using GitHub for code (and small data?)
- Using Figshare or Zenodo vs a lab website (DOIs, other reasons)
- Or using, most ideally, a library or other proper long-term data archival service
